When are Fuzzy Extractors Possible?

### 2014-10-02 trunk/info-bounds/FuzzyExtPossibility.tex
pass through introduction

\def\shownotes{1}
\def\blinded{0}

@@

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Usually, authentication requires some high quality secret.  Traditionally, this secret is assumed to have high min-entropy.  However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.  To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings. \lnote{Why limit to authentication}

 This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}. \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.  The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.

A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.  The $key$ should be uniform even if an adversary has observed $p$.  The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.  For any security the initial readings must come from a high min-entropy distribution $W$.

\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
& Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.  Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Semantically secure multi-linear encodings are a very strong assumption and unpredictability is weaker than pseudoentropy.  Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.

\paragraph{Our approach} Our secure sketch in the distribution aware setting relies on two observations.  First for distributions where every point has roughly the same probability, the fuzzy min-entropy is determined by the ball with the greatest number of points.  We call this type of distribution \emph{nearly flat}.  For nearly flat distributions, the goal is to disambiguate any point within a ball of radius $t$.  A universal hash with output length larger than the size of this ball suffices.  However, for an arbitrary distribution, we cannot afford to write down information proportion to the ball with the greatest number of points.  We solve this problem by converting an arbitrary distribution into a number of nearly flat distributions by writing down the probability of our original reading $w$.  Then in reconstruction we limit ourselves to points of this probability.  We then show this probability information is not two helpful.  We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level~(\consref{cons:leveling}).

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  In our negative results, we construct a family of distributions $\mathcal{W}$ where conditioned on seeing a single point, the support of the remainder of the distribution is uniform.  Informally, to provide security $\rep(\cdot, p)$ partitions the metric space.  Each part of this partition maps a single key.  We can split each part into interiors and boundaries. In the Hamming space, the boundary makes up the overwhelming majority of the space.  Thus, for most distributions $W$ the support of $W$ lies overwhelmingly in the boundary of these parts.  All points in the boundary can be effectively excluded, reducing the entropy of $W$

\bnote{I'm writing these, very rough draft}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We will also use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
\begin{definition}[Conditional Hartley Entropy]
\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  For the remainder of this work we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

@@

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.  This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  In the \emph{distribution-aware} setting, the algorithms only work for a distribution $W$.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.   
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.  That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious secure sketch for the elements of $V$.
\end{itemize}
\end{proof}
\subsubsection{Feasibility of computational secure sketches}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

>>>>

\def\shownotes{0}
\def\blinded{0}

@@

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Repeatable entropy sources enable applications cryptographic applications such as authentication and key agreement\bnote{more?}.  However, many entropic sources present a problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources it is often necessary to remove noise, and achieve the same value in subsequent readings.  \bnote{I tried to remove entropy from this but it needs to be cleaned up}

Bennett, Brassard, and Roberts~\cite{bennett1988privacy} introduced this problem in the interactive setting. \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.

The security requirement for fuzzy extractors that is $key$ uniform even to an adversary who has observed $p$.   Achieving a strong $\key$ is harder as the allowed error tolerance $t$ increases. It becomes easier for the adversary to guess a $w'$ within distance $t$ of $w$ and an adversary who guesses a nearby $w'$ can obtain $\key$ by running $\rep$.

\paragraph{A New Entropy Notion}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$. Suppose $w$ is sampled from a distribution $W$. If the adversary only had access to $\rep$, they would recover $\key$ with maximal probability by guessing $w'$ that maximizes the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$. We  define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_w' \Pr[W\in B_t(w')]$.

An adversary who can guess $w'$ can recover the $\key$, that is, $\Hav(\key|p) \le \Hfuzz(W)$.  Super-logarithmic fuzzy min-entropy is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  
Observe that, $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$.  However, the difference between these quantities is very large for practical settings.  As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}

\paragraph{A New Characterization}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather information-theoretic) security are possible in \secref{sec:related settings}.

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution rather than relying on cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
It is important to note that this characterization requires the fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.

\paragraph{A New Impossibility Result}

However, fuzzy extractor designs are typically not tailored to a particular source, but rather for a family sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

We showthat this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart. \lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.

\paragraph{Results on Information Reconciliation}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}). Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.

\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
 & Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}
\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.  Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.  We use universal hashing to disambiguate points.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).  We then write down the level and apply the above construction considering only points in that level.  We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  The value  $p$ partitions the metric space into possible and impossible $w$.  The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.  This is enough to contradict security for both secure sketches and fuzzy extractors.

\bnote{are these really affine lines?}
\bnote{I'm writing these, very rough draft}

\subsection{Sufficiency of $\Hfuzz$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result implies that $W|p$ cannot have pseudoentropy~(see \secref{sec:feas comp sec sketch} for discussion).

Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we describe the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
 Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
%\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

@@

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  In the \emph{distribution-aware} setting, the algorithms work for a single distribution $W$.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.  That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution over $\mathcal{V}$, there is distribution oblivious secure sketch for the elements of $V$.
\end{itemize}
\end{proof}
\subsubsection{Feasibility of computational secure sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.
